\documentclass[]{hieudo-build}
\begin{document}
\namesection{Saloni Bhartia}
{
\urlstyle{same}
	\faEnvelope \href{mailto:salonibhartia1996@gmail.com}{ salonibhartia1996@gmail.com}\\
	\faGithub \href{https://github.com/saloni1996}{ github.com/saloni1996}\\
	\faPhone  \href{}{91-9654804287}
}
\begin{minipage}[t]{0.3\textwidth} 

\section{Education} 

\subsection[Indira Gandhi Delhi Technical University For Women]{Indira Gandhi Delhi Technical University For Women}
\descript{Kasmere Gate, New Delhi, India}
Bachelor of Technology in Computer Science \\
Expected Grad. June 2018 \\
Percentage: 84.44\% \\
\sectionsep

\descript{Senior Secondary}
\subsection{Queen Mary's School}
\descript{Tis Hazari, New Delhi, India}
Grad. May 2014  
\\ Percentage: 95.80\%
\sectionsep

\section{Skills}
% \subsection{Programming}
\subsection[Subjects]{Subjects of knowledge:}
Machine Learning, Data Mining, Algorithms, Data Structures, Information Security.

\subsection[Languages]{Programming and Scripting Languages:}
C++, C, Python, HTML, CSS, PHP\\ 

\subsection[Frameworks]{Frameworks:}
Django \\

\subsection[Databases]{Databases:}
SQLite, MySQL \\

\subsection[Version Control]{Version Control:}
Git and Github\\
\sectionsep

\section{Experience}

\workplace{CryptoGirls}{Ongoing}\\
\position{Worked in Machine Learning for intrusion detection systems}{}
\vspace{0.9em} % Hacky fix for awkward extra vertical space

\workplace{Society for Technical Research and Industrial Development (S.T.R.I.De)}{Jun-Aug, 2015}\\
\position{\textit{Course Module Developer}}{ Worked on MIT app inventor to develop simple and handy android apps.}
\vspace{0.9em} 
\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

\section{Projects}

\runsubsection{RTI}
\descript{}
An automation of RTI application system, in government institutions, no commercial software available for the same. \\
\textbf{Link:} \url{https://github.com/saloni1996/RTI_Automation}
\sectionsep
\runsubsection{Eventley}
\descript{}
Analyzing the popularity of events based on the user location and his/her interest(like social,cultural and so on)\\
\textbf{Link:} \url{https://github.com/saloni1996/Eventley}
\sectionsep
\runsubsection{Gesture Controlled Robotic Vehicle}
\descript{}
An IOT based device, which controls the motor vehicle depending upon the gesture made by the driver of vehicle. Also integrated with cloud.\\
The link for its user inteface is: \textbf{Link:} \url{https://github.com/saloni1996/gesture-controlled-robotic-vehicle}
\sectionsep 
\runsubsection{Profile Site}
\descript{}
A profile site based on HTML, and CSS. \\
 \textbf{Link:} \url{https://github.com/saloni1996/gesture-controlled-robotic-vehicle}
\sectionsep
\runsubsection{For more projects:}
\descript{}
Check out my github repository for more projects:\url{https://github.com/saloni1996/}
\sectionsep

\section{Achievements}

\vspace{0.5em} 
\begin{tightemize}

\item Secured 2nd position in Software Hackathon, organised by IEEE.
\item Secured 3rd Position for a competetion, organised by IEEE under the name BUGWARS.
\item School Science Topper and received a certificate of appreciation for excellent performance in 12th class board by HRD minister.
\item Received Certificate of Merit for Physics, being among top 0.1\% of successful students
\end{tightemize}
\sectionsep


\section{Position of Responsibilities}

\vspace{0.5em} 
\begin{tightemize}
\item Mentor at DjangoGirls Delhi, mentored budding engineers on Django and Python.
\item Organizer of Mozilla Campus Club events and an active speaker on various technological topics, like HTML, CSS, Machine Learning and as like.
\item Speaker at ElasticSearch and Pyladies event on Git and Github, its importance and the opportunities offered in open source.
\item Core team member of Django Girls Delhi, and ElasticSearch Delhi team.
\item Associate Team Member for Website Development team for technical fest, INNERVE'16 in college.
%\item SpicMacay Volunteer, promoting the importance of cultural events in college.
%\item Coordinator at editorial team at college technical fest, TREMORS’15.
\end{tightemize}
\sectionsep


\end{minipage} 

\end{document}